### 2023-06-23 python_excel_ite.tex
intro section drafted

Numerous R and Python based data science courses have been developed and offered at universities and through online learning platforms such as Coursera, EdX, Udemy and others. Some of these courses have made a large amount of their course content freely available for self-learners and for other educators. At our institution, we have had a spreadsheet based modeling course in place since 2001. In 2015, we created a course called Practical Computing for Data Analytics (PCDA) that introduced both R and Python (along with a little Linux) for use in data analytics work. The course is taught using a combination of R Markdown documents \cite{bibid} and Jupyter notebooks \cite{bibid}. Both of these support \textit{literate computing} \cite{Jupyter_proposal} and allow us to create educational narratives that support iterative exploration and development. The ability to weave standard language with formal programming languages has made notebook computing a defacto standard in the data science education community. All of the course content, including many Jupyter notebooks and supporting screencasts, is freely available from a publicly accessible course web site \url{URL}.

@@

\begin{itemize}
	\item Teach relevant Python to business students using familiar and relevant modeling examples,
	\item Give sense of software development process and design decisions
	\item Model a learning journey
	\item Teach students to think and act like a software developer, not just an analyst
\end{itemize}

One criticism that has been levied against data science programs has been the lack of attention to basic software engineering principles. The image of newly minted grads developing spaghetti coded Jupyter notebooks not nearly ready for being put into production has reached meme like status. I hoped to address some of these issues in the EwP module. Sneakily, students would be exposed to some simple software engineering concepts during the process of building and analyzing familiar models. This is really no different than the integration of advanced Excel functions and techniques with spreadsheet modeling tutorials. Just as spreadsheet modeling students were able to easily wow their coworkers and managers with INDEX-MATCH and intermediate Pivot Table skills, I hoped that my students ability to properly document a Python function and use git and GitHub would pay off in the workplace.

@@

The EwP module is made up of three submodules. The first of these focuses on building and using a typical spreadsheet model using Python. Then the functionality developed for doing this type of modeling in Python is deployed as a reusable package. We end with an introduction to using Python to manipulate Excel files, an extremely common use case.

All of the Python modules in the PCDA course as well as the entire AAP course are taught using a combination of Jupyter notebooks, Python scripts, and videos walking through the notebooks, all publicly accessible from extensive course web pages. GIVE URL. Some background on Jupyter notebooks for analytics - see downloaded papers. Questions and coding challenges sprinkled throughout the notebooks - answers at bottom. While AAP is online asynch, this same approach has been used very successfully in a computer teaching lab for the PCDA course. The screencasts are highly valued by the students as they can rewatch things as needed. Many are working professionals and a 2.5 hour evening class in a warm computer lab can be taxing.

>>>>

Numerous R and Python based data science courses have been developed and offered at universities and through online learning platforms such as Coursera, EdX, Udemy and others. Some of these courses have made a large amount of their course content freely available for self-learners and for other educators. At our institution, we have had a spreadsheet based modeling course in place since 2001. In 2015, we created a course called Practical Computing for Data Analytics (PCDA) that introduced both R and Python (along with a little Linux) for use in data analytics work. The course is taught using a combination of R Markdown documents \cite{bibid} and Jupyter notebooks \cite{bibid}. Both of these support \textit{literate computing} \cite{Jupyter_proposal} and allow us to create educational narratives that support iterative exploration and development. The ability to weave standard language with formal programming languages has made notebook computing a defacto standard in the data science education community. All of the PCDA course content, including many Jupyter notebooks and supporting screencasts, is freely available from a publicly accessible course web site \url{URL}.

@@

\begin{itemize}
	\item teach relevant and more advanced Python to business students using familiar and simple modeling examples,
	\item convey a sense of the software design and development process,
	\item be a tour guide for a learning journey,
	\item teach students to think and act like a software developer, not just an analyst.
\end{itemize}

One criticism that has been levied against data science programs has been the lack of attention to basic software engineering principles. The image of newly minted grads developing spaghetti coded Jupyter notebooks not nearly ready for being put into production has reached meme like status. I hoped to address some of these issues in the EwP module. Sneakily, students would be exposed to some simple software engineering concepts during the process of building and analyzing familiar models. This is really no different than the integration of advanced Excel functions and techniques with spreadsheet modeling tutorials. Just as spreadsheet modeling students were able to easily wow their coworkers and managers with INDEX-MATCH and intermediate Pivot Table skills, I hoped that my students ability to properly document a Python function and use git and GitHub would give them a little street cred.

@@

The EwP module is made up of three submodules. The first of these focuses on building and using a typical spreadsheet model using Python. Then the functionality developed for doing this type of modeling in Python is deployed as a reusable package. We end with an introduction to using Python to manipulate Excel files.

%TODO needs finishing
All of the Python modules in the PCDA course as well as the entire AAP course are taught using a combination of Jupyter notebooks, Python scripts, and videos walking through the notebooks, all publicly accessible from extensive course web pages. GIVE URL. Some background on Jupyter notebooks for analytics - see downloaded papers. Questions and coding challenges sprinkled throughout the notebooks - answers at bottom. While AAP is online asynch, this same approach has been used very successfully in a computer teaching lab for the PCDA course. The screencasts are highly valued by the students as they can rewatch things as needed. Many are working professionals and a 2.5 hour evening class in a warm computer lab can be taxing.
